### 2024-03-03 docs/manuscript/manuscript.qmd
update on ms and fig 1

### Two-Minutes Step Test

The TMST is a sub-test from the Senior Fitness Test, demanding a low to moderate intensity [@Rikli1999; @ijerph20054456]. The test consists of a two-minute assessment designed to evaluate cardiorespiratory fitness. Participants are instructed to raise their right knee to a marked point on a wall as many times as possible within the given time frame, ensuring that each raise reaches at least a 70° angle at the thigh-femoral joint.

@@

```{r}
#| echo: false
#| message: false
#| warning: false
library(flextable)
readRDS(file = "tables/tbl-descriptives.RDS") |> 
  font(part = "all", fontname = "Times")
```

@@

@@

In addition, a greater body fat percentage was negatively correlated with physical fitness (r = -0.273, p = 0.015).

@@

Physical fitness was positively correlated with a greater sympathetic activity during exercise, which was reflected by SNS index (r = 0.313, p = 0.006), mean HR (r = 0.355, p = 0.002) and its inverse counterpart mean R-R (r = -0.35, p = 0.002).

@@

## Mediation effects associated with

>>>>

<!--- ESTA VARIABLE NO ES MENCIONADA EN LOS RESULTADOS, ES CUESTIONABLE SU MENCIÓN EN EL PAPER --->
### Two-Minutes Step Test **RECONSIDERAR ESTA VARIABLE**

The TMST is a sub-test from the Senior Fitness Test, demanding a low to moderate intensity [@Rikli1999; @ijerph20054456]. The test consists of a two-minute assessment designed to evaluate cardiorespiratory fitness. Participants are instructed to raise their right knee to a marked point on a wall as many times as possible within the given time frame, ensuring that each raise reaches at least a 70° angle at the thigh-femoral joint.
<!--- ESTA VARIABLE NO ES MENCIONADA EN LOS RESULTADOS, ES CUESTIONABLE SU MENCIÓN EN EL PAPER --->

@@

```{r prep-env}
#| include: false
#| message: false
#| warning: false
library(flextable)
library(data.table)
load("../../data/mindfulness.RData")
```

```{r tbl-1}
#| echo: false
#| message: false
#| warning: false
readRDS(file = "tables/tbl-descriptives.RDS") |> 
  font(part = "all", fontname = "Times")
```
**Table 1**. Main sample characteristics. Body composition and sociodemograpic variables are displayed for the overall sample and aggregated by sex. Differences between males and females are displayed as SMD and CI~95%~ for continuous variables.

@@

![](figures/fig-1.jpeg)
**Figure 1**. Main correlations among psychological, cardiac autonomic and performance variables. Non-significant correlations (i.e., p > 0.05) were crossed with and "X". The more intense the color the stronger the correlation, either positive or negative.

@@

In addition, a greater body fat percentage was negatively correlated with the SPPB total score (r = -0.273, p = 0.015), menawhile, no other metrics of body composition were associated with physical performance of the SPPB (i.e., p > 0.05).

@@

Physical fitness, reflected through SPPB total score, was positively correlated with a greater sympathetic activity during exercise, which was reflected by SNS index (r = 0.313, p = 0.006), mean HR (r = 0.355, p = 0.002) and its inverse counterpart mean R-R (r = -0.35, p = 0.002).

@@

## Mediation

[Pendiente]
